Global patterns of forest autotrophic carbon fluxes

### 2020-08-05 manuscript/manuscript draft.Rmd
updates including hypothesis table

We show that C fluxes are broadly consistent in their responses to climate drivers on the global scale, with at most modest trends in C allocation among the variable pairs tested (Figs. 2, S3). 
This parallels the observation that C allocation across multiple C fluxes varies little with respect to climate along a steep tropical elevational gradient [@malhi_variation_2017; but see @moser_elevation_2011], 
and is not surprising given that trees face universal constraints in carbon allocation (**REFS**). 
The one trend in allocation that emerged from our analysis was a tendency for greater C allocation aboveground--and to foliage in particular--in warm tropical climates (Fig. S3). This is consistent with observations of increasing allocation to roots with declining temperature across a tropical elevational gradient [@moser_elevation_2011], 
and with observations and theory predicting relatively higher belowground carbon allocation at higher latitudes [@gill_belowground_2016].
It is also consistent with findings that as forest productivity increases, proportionaly more carbon is allocated to $ANPP_{foliage}$ relative to $BNPP_{fine.root}$ [@chen_allometry_2019] or $ANPP_{stem}$ [@hofhansl_new_2015]. **( check / comment on  @litton_carbon_2007 )**

>>>>

We show that C fluxes are broadly consistent in their responses to climate drivers on the global scale, with at most modest trends in C allocation among the variable pairs tested (Figs. 2, S3). 
This parallels the observation that C allocation across multiple C fluxes varies little with respect to climate along a steep tropical elevational gradient [@malhi_variation_2017; but see @moser_elevation_2011], 
and is not surprising given that trees face universal constraints in carbon allocation (**REFS**). 
The one trend in allocation that emerged from our analysis was a tendency for greater C allocation aboveground--and to foliage in particular--in warm tropical climates (Fig. S3). This is consistent with observations of increasing allocation to roots with declining temperature across a tropical elevational gradient [@moser_elevation_2011], 
and with observations and theory predicting relatively higher belowground carbon allocation at higher latitudes [@gill_belowground_2016]. **Krista -- I took out the ANPP:NPP graphs from the SI after looking back at what Helene said in issue #77 -- let me know if you think it's worth putting them back in wrt this point**
It is also consistent with findings that as forest productivity increases, proportionaly more carbon is allocated to $ANPP_{foliage}$ relative to $BNPP_{fine.root}$ [@chen_allometry_2019] or $ANPP_{stem}$ [@hofhansl_new_2015]. **( check / comment on  @litton_carbon_2007 )**
